|

### 2021-02-15 appendix/appendix.Rmd
copyediting appendix text

About 98% of the interviewees agreed to participate in the survey experiment.
We excluded respondents who did not give their consent from the dataset.

@@

The graphs shows that _crime_ (same as in English), _porque_ (because),
_linchamento_ (lynching), and _caso_ (case) are the words respondents use most
often. This is expected as subjects were asked to justify their choices. The
next words in the list are related to victim or crime characteristics, such as
_criança_ (child), _estupro_ (rape), _assassinato_ (murder), and _vítima_
(victim). Indeed, they provide evidence our previous findings and confirm that
respondents select lynching victim profiles according to these two factors.
Criminal characteristics, such as age or race, do not seem to be particularly
relevant, as respondents do not mention them as much. The following terms are
_nenhum_ (none), _contra_ (against), _acho_ (I think), _casos_ (cases), _ter_
(have to), and _justiça_ (justice). We believe these words correspond to cases
where respondents wanted to affirm they do not have any preference regarding
the lynching profiles, or that they would rather not have chosen any of the
alternatives.

@@

Our last model is a semisupervised LDA, in which we include a series of
keywords to measure how frequently some pre-defined topics appear often in the
responses. We adopt a conservative approach and only include words that we have
a high degree of confidence that are not ambiguous. There are four pre-defined
topics in this estimation. The first refers to victims, and include the
Portuguese words for _children_, _life_, and _victim_ (along with possible
variations). The second topic describes crime characteristics with words such
as _murder_, _rape_, _kill_, _molest_, and _steal_. The next group has four
keywords that describe lynching perpetrators, and they are _gangs_, _family_,
_bystanders_, and _police_. The fourth topic includes terms to identify
respondents who are against lynchings, and we added _against_, _none_, _do not
agree_, and _choice_ as the seed terms. We see that these groups have a large
number of terms each, and that crime characteristics is the topic that shows
more often when our terms are applied.

>>>>

About 98% of the interviewees agreed to participate in the survey experiment.
We excluded the remaining 2% from our analyses.

@@

The graphs shows that _crime_ (same as in English), _porque_ (because),
_linchamento_ (lynching), and _caso_ (case) are the words respondents use most
often. This is expected as subjects were asked to justify their choices. The
next words in the list are related to victim or crime characteristics, such as
_criança_ (child), _estupro_ (rape), _assassinato_ (murder), and _vítima_
(victim). Indeed, they provide evidence for our previous findings and confirm
that respondents select lynching victim profiles according to these two
factors. Criminal characteristics, such as age or race, do not seem to be
particularly relevant, as respondents do not mention them as much. The
following terms are _nenhum_ (none), _contra_ (against), _acho_ (I think),
_casos_ (cases), _ter_ (have to), and _justiça_ (justice). We believe these
words correspond to cases where respondents wanted to affirm that they do not
have any preference regarding the lynching profiles, or that they would rather
not have chosen any of the alternatives.

@@

Our last model is a semisupervised LDA, in which we include a series of
keywords to measure how frequently some pre-defined topics appear often in the
responses. We adopt a conservative approach and only include words that we have
a high degree of confidence that are not ambiguous. There are four pre-defined
topics in this estimation. The first refers to victims, and include the
Portuguese words for _children_, _life_, and _victim_ (along with possible
variations). The second topic describes crime characteristics with words such
as _murder_, _rape_, _kill_, _molest_, and _steal_. The next group has four
keywords that describe lynching perpetrators, and they are _gangs_, _family_,
_bystanders_, and _police_. The fourth topic includes terms to identify
respondents who are against lynchings, and we added _against_, _none_, _do not
agree_, and _choice_ as seed terms. We see that the topic describing crime
characteristics is the one that appears more often.
